\textit{Completeness of resonance states for quantum graph with two semi-infinite edges}

### 2017-02-01 complet_wires_cvee1.tex
Fixed typos

The paper is devoted to investigation of resonance states for
scattering system. The problem of resonances is intensively
studied due to its importance for physical applications (see,
e.g., \cite{ELT,APV,DEM,E,EK,Ch} and references in \cite{Pav})
There is an interesting question concerning to the completeness of
the system of such states. An example of such problem is related
to scattering by bounded obstacle
\cite{BG,HM,Gad,P90,P92,PP93,PP93a}. First, let us consider
bounded resonator $\Omega$ with smooth boundary, i.e. the Neumann
or Dirichlet Laplacian in this domain. It has the discrete
spectrum and the system of it's eigenstates is complete in
$L_2(\Omega)$. Then, consider an analogous resonator coupled with
the outer space ${\mathbb R}^3\setminus\Omega$ through a small
window. In this case the spectrum changes drastically. The
discrete spectrum disappears, in general. More precisely,
eigenvalues converge to quasi-eigenvalues (resonances) and
eigenstates - to resonance states which are similar to eigenstates
(i.e. satisfy the equation ant the boundary conditions bur do not
belong to  $L_2(\Omega\cup ({\mathbb R}^3\setminus\Omega))$).
Nevertheless, restrictions of the resonance states on $\Omega$
belong to $L_2(\Omega)$, and one can pose a question: Is the
system of the resonance states complete in $L_2(\Omega)$? At
present, there is no general answer. Our hypothesis (see
\cite{PP17}) is that the maximal appropriate domain is the convex
hull of the scatterer. In the present paper we deal with a quantum
graph (see Fig. \ref{fig:res_bundle}) having some common features
with the scattering system described above. The role of resonator
$\Omega$ is played by a number of edges connected two vertices.
Quantum graphs with included resonators were considered in a few
papers (see, e.g., \cite{BG,GEIP,EIP}). Although the number of
works concerning to resonances is very large, the problem of
resonance states completeness were considered rarely
\cite{Sh,pops,VP}. We can mention a few works in which the problem
of resonance states completeness was not declared but, really, it
was investigated (see, e.g., \cite{AIR,AI,MAAE,MM} and references
therein). As for completeness of resonance states for quantum
graph, we do not no other works dealing with this problem.

@@

Now, let us fix $r$, and further, for the sake of readability, we
define $C = C(r)$ and $R = R(r)$. To estimate the integral, we use
Cauchy-Schwarz's inequality:
\[
\big| \langle u,v \rangle \big| \leq \left\|u\right\|
\left\|v\right\|,
\]
or to be precise, it's $\mathcal{L}^2[a, b]$ version:
\[
\left| \int\limits_{t=a}^{b} f(t) g^*(t) dt \right| \le
\sqrt{\int\limits_{t=a}^b \left|f(t)\right|^2 dt }
\sqrt{\int\limits_{t=a}^b \left|g(t)\right|^2 dt }.
\]
%
To use the inequality, we are going to represent the integrand in
(\ref{eq:critp}) as $f(t) g^*(t)$ as follows ($a = 0, b = 2 \pi$):
\begin{equation}\label{eq:split}
f(t)   = \ln s(R e^{\mathrm{i} t} + \mathrm{i} C)
\frac{\sqrt{R}}{R e^{\mathrm{i} t} + \mathrm{i} C + i},\quad
g^*(t) = \frac{\sqrt{R}}{R e^{\mathrm{i} t} + \mathrm{i} C + i}
\end{equation}
Next, we will show that $\|g\|$ (that is, $\sqrt{\int_0^{2\pi}
\left|g(t)\right|^2}$) is bounded by a constant which does not
depend on $r$, and $\|f\|$ goes to $0$ as $r$ goes to $1$, hence
(\ref{eq:critp}) tends to zero.

\subsection{Estimating of $\|g\|$}

@@

\subsection{Estimating of $\|f\|$}
To proof the convergence, we will take into account the following
facts concerning to function $s(k)$ (\ref{eq:bundle_s}):

@@

\subsubsection{Simplifying of $s(k)$}

We build a simple estimate for $s(k)$ over the upper complex
plane. This function will be independent of the complex part of
its argument which will make the analysis way easier.

>>>>

The paper is devoted to investigation of resonance states for
scattering system. The problem of resonances is intensively
studied due to its importance for physical applications (see,
e.g., \cite{ELT,APV,DEM,E,EK,Ch} and references in \cite{Pav})
There is an interesting question concerning to the completeness of
the system of such states. An example of such problem is related
to scattering by bounded obstacle
\cite{BG,HM,Gad,P90,P92,PP93,PP93a}. First, let us consider
bounded resonator $\Omega$ with smooth boundary, i.e. the Neumann
or Dirichlet Laplacian in this domain. It has the discrete
spectrum and the system of its eigenstates is complete in
$L_2(\Omega)$. Then, consider an analogous resonator coupled with
the outer space ${\mathbb R}^3\setminus\Omega$ through a small
window. In this case the spectrum changes drastically. The
discrete spectrum disappears, in general. More precisely,
eigenvalues converge to quasi-eigenvalues (resonances) and
eigenstates converge to resonance states which are similar to eigenstates
(i.e. satisfy the equation ant the boundary conditions bur do not
belong to  $L_2(\Omega\cup ({\mathbb R}^3\setminus\Omega))$).
Nevertheless, restrictions of the resonance states on $\Omega$
belong to $L_2(\Omega)$, and one can pose a question: is the
system of the resonance states complete in $L_2(\Omega)$? At
present, there is no general answer. Our hypothesis (see
\cite{PP17}) is that the maximal appropriate domain is the convex
hull of the scatterer. In the present paper we deal with a quantum
graph (see Fig. \ref{fig:res_bundle}) having some common features
with the scattering system described above. The role of resonator
$\Omega$ is played by a number of edges connected two vertices.
Quantum graphs with included resonators were considered in a few
papers (see, e.g., \cite{BG,GEIP,EIP}). Although the number of
works concerning to resonances is very large, the problem of
resonance states completeness were considered rarely
\cite{Sh,pops,VP}. We can mention a few works in which the problem
of resonance states completeness was not declared but, really, it
was investigated (see, e.g., \cite{AIR,AI,MAAE,MM} and references
therein). As for completeness of resonance states for quantum
graph, we are not aware of other works dealing with this problem.

@@

Now, let us fix $r$, and further, for the sake of readability, we
define $C = C(r)$ and $R = R(r)$. To estimate the integral, we use
Cauchy-Schwarz's inequality:
\[
\big| \langle u,v \rangle \big| \leq \left\|u\right\|
\left\|v\right\|,
\]
or to be precise, its $\mathcal{L}^2[a, b]$ version:
\[
\left| \int\limits_{t=a}^{b} f(t) g^*(t) dt \right| \le
\sqrt{\int\limits_{t=a}^b \left|f(t)\right|^2 dt }
\sqrt{\int\limits_{t=a}^b \left|g(t)\right|^2 dt }.
\]
%
To use the inequality, we are going to represent the integrand in
(\ref{eq:critp}) as $f(t) g^*(t)$ as follows ($a = 0, b = 2 \pi$):
\begin{equation}\label{eq:split}
f(t)   = \ln s(R e^{\mathrm{i} t} + \mathrm{i} C)
\frac{\sqrt{R}}{R e^{\mathrm{i} t} + \mathrm{i} C + i},\quad
g^*(t) = \frac{\sqrt{R}}{R e^{\mathrm{i} t} + \mathrm{i} C + i}
\end{equation}
Next, we will show that $\|g\|$ (that is, $\sqrt{\int_0^{2\pi}
\left|g(t)\right|^2}$) is bounded by a constant which does not
depend on $r$, and $\|f\|$ goes to $0$ as $r$ goes to $1$, hence
(\ref{eq:critp}) tends to zero.

\subsection{Estimate of $\|g\|$}

@@

\subsection{Estimate of $\|f\|$}
To proof the convergence, we will take into account the following
facts concerning to function $s(k)$ (\ref{eq:bundle_s}):

@@

\subsubsection{Simplifying $s(k)$}

We are going to build a simple estimate for $s(k)$ over the upper complex
plane. This estimate will be independent of the complex part of
its argument which will make the analysis way easier.
